Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2019-03-02 documentation/report.tex
Final edits

My objective was to develop a set of machine learning techniques that resolve these two problems, and thus more efficiently generate highly accurate classifiers.

@@

In DEAP-3600, photons are absorbed by a wavelength shifting medium and re-emitted in an unpredictable direction, before being detected by one of 255 photomultiplier tubes (PMTs) on the surface of the spherical detector. The randomness severely limits the accuracy of conventional classifiers; the best so far removes 99.6\% of alpha background radiation, while also (undesirably) removing 91.0\% of WIMP events. Because of physical limitations, simulated data is used for calibration, with 30 real-world experimental events available for testing.

@@

\subsection{PICO-60}

@@

\begin{figure}[ht]
    \centering
    \fbox{\includegraphics[width=0.85\textwidth]{pico_final_results}}
    \caption{\label{pico_final_results} Validation accuracy, precision, recall, and loss for each technique in PICO-60. Error bars represent the 8th and 92nd percentiles.}
\end{figure}

\subsection{DEAP-3600}

@@

This successful network model was further tested on the limited amount of available real-world experimental data. It removed 73.9\% of WIMP-like (neutron calibration) events, which is in line with the 75.7\% obtained on simulated data.

@@

These results confirm that I met my objective: my new techniques resolved the two fundamental challenges I identified, permitting significantly improved performance, requiring little manual analysis or optimization.

>>>>

My objective was to develop a set of machine learning techniques that address these two problems, and thus more efficiently generate highly accurate classifiers.

@@

In DEAP-3600, photons are absorbed by a wavelength shifting medium and re-emitted in an unpredictable direction, before being detected by one of 255 photomultiplier tubes (PMTs) around the spherical detector. The randomness severely limits the accuracy of conventional classifiers; in a simulation, the best so far removes 99.6\% of alpha background, while also (undesirably) removing 91.0\% of WIMP events. Because of physical limitations, simulated data is used for calibration, with 30 real-world experimental events available for testing.

@@

@@

\begin{figure}[ht]
    \centering
    \fbox{\includegraphics[width=0.95\textwidth]{pico_final_results}}
    \caption{\label{pico_final_results} Validation accuracy, precision, recall, and loss for each technique in PICO-60. Error bars represent the 8th and 92nd percentiles.}
\end{figure}

@@

This successful network model was further tested on the limited amount of available real-world experimental data. It removed 73.9\% of WIMP-like (neutron calibration) events,

which is in line with the 75.7\% obtained on simulated data.

@@

These results confirm that I met my objective: my new techniques successfully addressed the two fundamental challenges I identified, permitting significantly improved performance, requiring little manual analysis or optimization.
